Bayesian multi-proxy reconstruction of early Eocene latitudinal temperature gradients

### 2023-09-22 manuscript/main.qmd
remove leading spaces from results

The Eocene temperature gradient reconstructed with our Bayesian model is starkly different from the modern (Fig. 4). Modelled, median equatorial temperatures are `r tdiff_lat0$"50%"` (95% CI: `r tdiff_lat0$"2.5%"` -- `r tdiff_lat0$"97.5%"`)&deg;C higher for the EECO, and polar temperatures are `r tdiff_lat90$"50%"` (`r tdiff_lat90$"2.5%"` -- `r tdiff_lat90$"97.5%"`)&deg;C higher. This results in a flattened latitudinal temperature gradient of `r eocene_gradient$"50%"` (`r eocene_gradient$"2.5%"` -- `r eocene_gradient$"97.5%"`)&deg;C for the EECO, as opposed to `r modern_gradient$"50%"`&deg;C for the modern. To facilitate the comparison with latitudinal gradients reported in the literature, which sometimes do not report temperatures at very high latitudes, we report also the EECO gradient between the equator and the modern-day polar circle (66.6&deg;), which is slightly lower at `r eocene_gradient_polar_circle$"50%"` (`r eocene_gradient_polar_circle$"2.5%"` -- `r eocene_gradient_polar_circle$"97.5%"`)&deg;C.

>>>>

The Eocene temperature gradient reconstructed with our Bayesian model is starkly different from the modern (Fig. 4). Modelled, median equatorial temperatures are `r tdiff_lat0$"50%"` (95% CI: `r tdiff_lat0$"2.5%"` -- `r tdiff_lat0$"97.5%"`)&deg;C higher for the EECO, and polar temperatures are `r tdiff_lat90$"50%"` (`r tdiff_lat90$"2.5%"` -- `r tdiff_lat90$"97.5%"`)&deg;C higher. This results in a flattened latitudinal temperature gradient of `r eocene_gradient$"50%"` (`r eocene_gradient$"2.5%"` -- `r eocene_gradient$"97.5%"`)&deg;C for the EECO, as opposed to `r modern_gradient$"50%"`&deg;C for the modern. To facilitate the comparison with latitudinal gradients reported in the literature, which sometimes do not report temperatures at very high latitudes, we report also the EECO gradient between the equator and the modern-day polar circle (66.6&deg;), which is a lot lower at `r eocene_gradient_polar_circle$"50%"` (`r eocene_gradient_polar_circle$"2.5%"` -- `r eocene_gradient_polar_circle$"97.5%"`)&deg;C.
